%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer (Technical Lead)} % Job title
    {Well Dot, Inc.} % Organization
    {Remote} % Location
    {Sep. 2022 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Initiated and orchestrated the conversion of more than 200,000 lines of legacy JavaScript to TypeScript.}
        \item {Mentored engineers in TypeScript, emphasizing consistent application of best practices and type correctness.}
        \item {Provisioned an easily manageable monolithic infrastructure in AWS ECS + Fargate using Terraform, focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Built fully automated CI/CD pipelines with Gitlab CI for containerized applications using Docker and AWS ECR.}
        \item {Developed and deployed a containerized NestJS API to AWS ECS, resulting in the consolidation of code, drastically improving developer velocity.}
        \item {Shared ownership for the the maintenance and improvement of more than 20 mission-critical AWS Lambda microservices.}
        \item {Created Gitlab CI and Terraform workflows to delpoy lambda functions from a monorepo.}
        \item {Tested both Lambda functions and NestJS monolith for correct behavior using jest and supertest to cover unit, integration, and functional layers.}
        \item {Facilitated multiple process improvements, including the standardization organization-wide ESLint, TypeScript, and jest configurations.}
        \item {Wrote and maintained HIPAA-compliant applications and infrastructure.}
        \item {Interviewed senior-level engineering applicants, screening for technical capabilities in a cloud-native environment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Triplebyte} % Organization
    {Remote} % Location
    {Nov. 2021 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on a custom cheating detection system for code submissions capable of numerically quantifying similarity in $O(1)$ space and $O(n)$ time. The system achieved a 0\% false positive rate and increased consumer confidence in the accuracy of code assessments.}
        \item {Owned the implementation and maintenance of large-scale full-stack applicant screening features in Ruby on Rails and React (TypeScript).}
        \item {Optimized Postgres queries using Arel (a Relational Algebra for Ruby), reducing costs and improving performance and stability.}
        \item {Implemented complex Figma designs using React, Redux, and TailwindCSS, collaborating directly with product owners and designers to optimize the UX of the final product.}
        \item {Tested application for correct behavior with Cypress, Jest, and rspec, achieving 80\% test coverage for owned features.}
        \item {Outperformed the average developer velocity for the team by more than 100\% by self-directing and optimizing own workstreams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (Project Lead)} % Job title
    {Appstem} % Organization
    {Remote} % Location
    {Jun. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Primary customer-facing technical contact and engineer in developing a custom full-stack React Native mobile app using Google Firebase for cloud-native backend deployment for a high-value client.}
        \item {Developed more than 30 custom React Native (TypeScript) components and resolved dozens of bugs in KFC's mobile ecommerce app over the duration of a 2-month subcontract.}
        \item {Collaborated with lead designer to produce React Native components for Mazoola, a family-safe digital wallet.}
        \item {Tested mobile/web applications and their backends for correct functional behavior using jest and Detox.}
        \item {Implemented an in-app store for a React Native fitness application using Google Firebase and Stripe.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {eQ Technologic} % Organization
    {Costa Mesa, CA \cdotp Remote} % Location
    {Jul. 2019 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed, and maintained 20 separate custom client-specified web applications in vanilla ES5 JavaScript and Backbone.js.}
        \item {Leveraged Spring framework in Java and Kotlin to develop backends capable of managing HIPAA-compliant internal employee healthcare data.}
        \item {Implemented an Angular frontend to facilitate the entry of health coverage requests from employees.}
      \end{cvitems}
    }

\end{cventries}
